Towards a Universal Facebook of the Ancient World

### 2016-01-24 source/18/EAGLE2016_Full_Paper_Broux-XeLaTEX.tex
Some overfull hboxes fixed on paper 18 (Broux)

\usepackage{polyglossia}

@@

@@

\noindent Like Facebook, however, Trismegistos wants to grow, and get the entire ancient world on board. To achieve this goal,
Trismegistos' core database, the text database, must first be expanded by broadening its chronological and geographic
horizon. Since 2013 the team has been actively working toward the inclusion of all texts from antiquity in
Trismegistos. This implies including Latin and Greek inscriptions, an estimated 700,000 texts. Contacts with the Latin
epigraphic database in Heidelberg resulted in Trismegistos' participation in the Europeana EAGLE project, coordinating
the disambiguation across all partners. This added about 150,000 new texts to the Trismegistos database. The remaining
300,000 will be integrated from another source (Clauss-Slaby: \url{www.manfredclauss.de}), so that the coverage of Latin will
soon be exhaustive. For Greek, good contacts have been established with the main players in the field (PHI:
\url{epigraphy.packhum.org/inscriptions/}; DC3 [i.e. Duke, SEG, Claros]: \url{blogs.library.duke.edu/dcthree/}), and the aim is to
become partners in a project dealing with the 250,000 or so inscriptions during the next year. At the same time
Trismegistos is also working towards a complete coverage of indigenous languages and scripts, which are often separate
fields, isolated from the `classical' world. New partnerships for Etruscan have been set up, and soon also for Punic
(CIP: \url{cip.cchs.csic.es}) and South-Arabian (DASI: \url{dasi.humnet.unipi.it}), while for the Italic languages, for Gallic,
Lepontic, Venetic, and Messapian information has already been digitized on the basis of existing corpora.

@@

\noindent With the experience obtained during the extraction of names from the Greek papyri, Named Entity Recognition will be
applied to the Latin inscriptions incorporated in Trismegistos so far. This will result in the addition of an estimated
500,000 or more new references to names/individuals to Trismegistos People. Network analysis will be used to help with
the disambiguation of individuals.

>>>>

\usepackage{polyglossia}
\usepackage{ucharclasses}
\usepackage{microtype}

@@

%\begin{hyphenrules}{english}
%\hyphenation{na-mes/in-di-vi-du-als}
%\end{hyphenrules}

@@

\noindent Like Facebook, however, Trismegistos wants to grow, and get the entire ancient world on board. To achieve this goal,
Trismegistos' core database, the text database, must first be expanded by broadening its chronological and geographic
horizon. Since 2013 the team has been actively working toward the inclusion of all texts from antiquity in
Trismegistos. This implies including Latin and Greek inscriptions, an estimated 700,000 texts. Contacts with the Latin
epigraphic database in Heidelberg resulted in Trismegistos' participation in the Europeana EAGLE project, coordinating
the disambiguation across all partners. This added about 150,000 new texts to the Trismegistos database. The remaining
300,000 will be integrated from another source (Clauss-Slaby: \url{www.manfredclauss.de}), so that the coverage of Latin will
soon be exhaustive. For Greek, good contacts have been established with the main players in the field (PHI:
\url{epigraphy.packhum.org/inscriptions/}; DC3 [i.e. Duke, SEG, Claros]: \url{blogs.library.duke.edu/dcthree/}), and the aim is to
become partners in a project dealing with the 250,000 or so inscriptions during the next year. At the same time
Trismegistos is also working towards a complete coverage of indigenous languages and scripts, which are often separate
fields, isolated from the `classical' world. New partnerships for Etruscan have been set up, and soon also for Punic
(CIP: \url{http://cip.cchs.csic.es/}) and South-Arabian (DASI: \url{http://dasi.humnet.unipi.it/}), while for the Italic languages, for Gallic,
Lepontic, Venetic, and Messapian information has already been digitized on the basis of existing corpora.

@@

\noindent With the experience obtained during the extraction of names from the Greek papyri, Named Entity Recognition will be
applied to the Latin inscriptions incorporated in Trismegistos so far. This will result in the addition of an estimated
500,000 or more new references to names / individuals to Trismegistos People. Network analysis will be used to help with
the disambiguation of individuals.
